What is an Ancestral Recombination Graph?

### 2022-01-11 paper.tex

\begin{figure}
\vspace{5em}
\caption{\label{fig-recombination-nodes}
Recombination nodes are optional in an edge-annotated ARG. (A) A simulated
ARG including all recombination nodes. (B) The same ARG with recombination
nodes removed. (C) The corresponding sequence of trees.
}
\end{figure}

>>>>

\begin{figure}
\centering
\vspace{5em}
\includegraphics[width=\linewidth]{illustrations/ARG_recomb_node_deletion}
\caption{\label{fig-recombinati on-nodes}
Recombination nodes are optional in an edge-annotated ARG. (a) A simulated
ARG including all recombination nodes (red). (b) The same ARG having removed both
recombination nodes and nodes of common ancestors in which no genetic
lineages coalesce (cyan). (c) The sequence of trees corresponding to (b): if we were
to plot out the trees corresponding to (a) we would have more trees, but the topologies
and MRCA nodes at each genomic location would be identical. For clarity, nodes are
plotted by ranked time rather than true time on the y-axis.
% HYW: note that we also truncate nodes for portions in which they are unary,
% so that nodes which are coalescent nodes over only some of their length
% (blue-green) become coalescent nodes over their entire length (green). This
% can, however, throw away some useful information, for example node 4 has
% only a single parent edge in (a), but 2 parent edges (one of which appears
% to bypass node 11) in (b). In fact, this edge should go through node 11, but
% there may be no way to detect this from real data.
}
\end{figure}
